Computable Compressed Matrices\\Suplementary Material

### 2013-12-03 manuscript.tex
Adicionando as últimas figuras

The efficiency of the VLB method is influenced by the relative size of the 
bit-length groups. In this first example, we considered only two groups, each 
comprised of half the matrix elements. Let's now vary the relative frequency of 
the groups, $\frac{f_i}{rc}$, while sticking to two groups. Let's 
also\todo{Acho que tinha que tirar esse Let's also, talvez colocar Now, we are 
going to} assume that $\frac{f_i}{rc}$ is a good approximation to the 
probability of a given bit-length in a matrix, which we will denote by $p_i$.

@@

Observe que os bits posicionados mais à esquerda devem ser utilizados para 
informar que o número é o -5. Para efeito de otimização da biblioteca, foi 
escolhido a conversão dos números negativos para positivos e a utilização de 1 
bit para representar o sinal.

@@

Inserir os resultados

@@

An example of the application of the methodology presented is shown in Figure \ref{cf}. In this figure, the matrix with 
normal and bitstring formats are displayed. In both matrices, the information is represented and can be accessed. 
Therefore, it becomes possible to apply the selected algorithms.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.4,trim=5cm 0cm 5cm 0cm,clip]{cf}
  \caption{Illustration of the process of the bistring model application to matrices of collaborative filttering of the 
algorithms per use average (PUA) and of the bias from mean (BFM) in a matrix represented in the traditional and 
bitstring formats.}
  \label{cf}
\end{figure}

Inserir o segundo conjunto de resultados aqui.

@@

@@

>>>>

The efficiency of the VLB method is influenced by the relative size of the 
bit-length groups. In this first example, we considered only two groups, each 
comprised of half the matrix elements. Let's now vary the relative frequency of 
the groups, $\frac{f_i}{rc}$, while sticking to two groups. Let's 
also \todo{Acho que tinha que tirar esse Let's also, talvez colocar Now, we are 
going to} assume that $\frac{f_i}{rc}$ is a good approximation to the 
probability of a given bit-length in a matrix, which we will denote by $p_i$.

@@

@@

XXXXXXXXX

@@

An example of the application of the methodology presented is shown in Figure \ref{fig22}. In this figure, the matrix 
with normal and bitstring formats are displayed. In both matrices, the information is represented and can be accessed. 
Therefore, it becomes possible to apply the selected algorithms.

yyyyyyyyyyyyyy

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.4,trim=5cm 0cm 5cm 0cm,clip]{fig22}
  \caption{Illustration of the process of the bistring model application to matrices of collaborative filttering of the 
algorithms per use average (PUA) and of the bias from mean (BFM) in a matrix represented in the traditional and 
bitstring formats.}
  \label{fig22}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6,clip]{fig23}
  \caption{Tempo de processamento do método Per User Average em função do número de linhas de uma matriz com 3,000 
colunas. A linha verde na vetical indica que o momento aproximado que o método tradicional demanda acesso a disco para 
armazenar a matriz a ser analisada, onerando o processo. O método de bitstring consegue representar a matriz 
integralmente na memória, sem a necessiada de acesso a disco.}
  \label{fig23}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6,clip]{fig24}
  \caption{Tempo de processamento do método Per User Average em função do número de linhas de uma matriz com 3,000 
colunas. A linha verde na vetical indica que o momento aproximado que o método tradicional demanda acesso a disco para 
armazenar a matriz a ser analisada, onerando o processo. Para dimensões inferiores a aproximadamente 400 liinhas, o 
método tracional é mais rápido que o de bitstring, ressaltando que o custo computacional dos dois métodos é linear.}
  \label{fig24}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6,clip]{fig25}
  \caption{Relação entre o tempo de processamento pelo método de bisttring e o método tracional em função do número de 
linhas de uma matriz com 3,000 colunas. Verifica-se que para a matriz com um número inferior a aproximadamente 400 
linhas, o método tradicional é mais rápido, porém quando o número de linhas é superior, o método de bitstring é mais 
rápido, por causa da representação compactada em  memória da matriz.}
  \label{fig25}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6,clip]{fig26}
  \caption{xxx.}
  \label{fig23}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6,clip]{fig27}
  \caption{xxx.}
  \label{fig24}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6,clip]{fig28}
  \caption{xxx.}
  \label{fig25}
\end{figure}

\begin{figure}[h]
  \centering
  \subfigure[$A=5$]{
  \includegraphics[scale=0.4,clip]{fig29}
  }
  \subfigure[$A=A+5$]{
  \includegraphics[scale=0.4,clip]{fig30}
  }
  \subfigure[$A=A+A$]{
  \includegraphics[scale=0.4,clip]{fig31}
  }
  \subfigure[$A=A-8$]{
  \includegraphics[scale=0.4,clip]{fig32}
  }
  \caption{Z}
  \label{fig:29303132}
\end{figure}

\begin{figure}[h]
  \centering
  \subfigure[$A=5$]{
  \includegraphics[scale=0.4,clip]{fig33}
  }
  \subfigure[$A=A+5$]{
  \includegraphics[scale=0.4,clip]{fig34}
  }
  \subfigure[$A=A+A$]{
  \includegraphics[scale=0.4,clip]{fig35}
  }
  \subfigure[$A=A-8$]{
  \includegraphics[scale=0.4,clip]{fig36}
  }
  \caption{Z}
  \label{fig:33343536}
\end{figure}

\begin{figure}[h]
  \centering
  \subfigure[$A=5$]{
   \includegraphics[scale=0.4,clip]{fig37}
  }
  \subfigure[$A=A+5$]{
   \includegraphics[scale=0.4,clip]{fig38}
  }
  \subfigure[$A=A+A$]{
   \includegraphics[scale=0.4,clip]{fig39}
  }
  \subfigure[$A=A-8$]{
   \includegraphics[scale=0.4,clip]{fig40}
  }
  \caption{R}
  \label{fig:37383940}
\end{figure}

\begin{figure}[h]
  \centering
  \subfigure[$A=5$]{
   \includegraphics[scale=0.4,clip]{fig41}
  }
  \subfigure[$A=A+5$]{
   \includegraphics[scale=0.4,clip]{fig42}
  }
  \subfigure[$A=A+A$]{
   \includegraphics[scale=0.4,clip]{fig43}
  }
  \subfigure[$A=A-8$]{
   \includegraphics[scale=0.4,clip]{fig44}
  }
  \caption{R}
  \label{fig:41424344}
\end{figure}

@@

\newpage
